---
title: "linreg"
author: "mubarak Hussain"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linreg}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Description

 lab4 group 26.

# Import

```{r}
    library(lab4g26)
```

# Methods

To start with, we can use the initialize method to input formula and data

```{r}
example <- linreg(formula = Petal.Length~Species, data = iris)
```

The `print()` method can print out the coefficients and coefficient names.

```{r}
example$print()
```

The `plot()` method can plot the following two plots using such packages as `ggplot2`, `gird` and `gridExtra`.

```{r}
example$plot()
```

The `resid()` method can return the vector of residuals.

```{r}
head(example$resid())
```

The `pred()` method can return the predicted values.

```{r}
head(example$pred())
```

The `coef()` method can return the coefficients as a named vector.

```{r}
example$coef()
```

The `summary()` method can present the coefficients with their standard error, t-value and p-value as well as the estimate of ˆσ and the degrees of freedom in linear regression model.

```{r}
example$summary()
```



